Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
Implementation Section
Paper edits

We have developed an application named {\em Kimbee} that aims to help the process of speech therapy in young children. Speech therapies are often expensive for schools and parents to maintain, especially with younger children who require more time than others. Our application does not replace the speech therapist, rather it supplements the therapy. Instead of being limited to short sessions, therapists can use {\em Kimbee} to have their students work at home as well as in the classroom. The therapist can then monitor the child's progress through our application and use this newly gained information to further tailor the therapy to individual students. This will save both time and money for school districts and parents who are paying for their child's therapy.

@@

The purpose of this paper and project is to make speech therapy more effective in English speaking children from age 5 to age 12. Children in this age group tend to average over a year involved in weekly speech therapy meetings to overcome a speech disorder \cite{Kreider:Intro}. It is also common for therapists to spend most of their time with students during these sessions or in the classroom because it is often hard to work with children remotely. A session usually consists of having the child repeat words back to the therapist in order to target a specific sound or phoneme. Common speech impediments in children are often caused by functional speech disorders, or trouble learning to make specific speech sounds \cite{Brown:Children}.

We chose to focus on `R' sounds as they are one of the more common mispronunciations found in our target age group \cite{Dodd:Children}. Most `R' disorders will commonly pronounce words as if the `R' was a `W'. An example would be pronouncing the word {\em ``rabbit''} as {\em ``wabbit''}. We use similar techniques as therapists use in their sessions in our online application. By having the child or user repeat a target several times until he or she is able to pronounce it correctly, we are emulating the in person setting that they are used to. Each time a word is spoken, an audio recording of the speech is documented and saved for the therapist to analyze at a later time. This process is then wrapped in game setting to make the process of saying and repeating words more enjoyable for children. This helps supplement the therapy, rather than aiming to replace it. We hope that this will cause a decrease in the amount of time that children will need to spend in therapy, which will help save the school district or parents more money.

@@

With the widespread use of the tablet and increasing availability of the Internet, several applications have been developed that are similar to {\em Kimbee}. Researchers at the University of Zaragoza have created a standalone tablet application that aims to remove the therapist from the treatment \cite{Carlos:Vocaliza}. The researchers created an application for children to speak words and receive feedback on whether the word they said matches what was on the screen. The model they used also requires the student to train his or her voice in order for it to be recognized and processed correctly. Because of this, the amount of time it would take a new student to get started is significant. Their application currently only supports the Spanish language, which would not be of much help to English speaking students. Our project's scope is almost much narrower. Our focus is to help the therapist spend higher quality time with his or her students by giving them additional information from the student's work outside the sessions.

@@

>>>>

We have developed an application named {\em Kimbee} that aims to help the process of speech therapy in young children. Speech therapy is often expensive for schools and parents to maintain, especially when children take abnorbmally long amounts of time to overcome their impediments. Our application does not replace the speech therapist rather it supplements the therapy. Instead of being limited to short sessions, therapists can use {\em Kimbee} to have their students work at home as well as in the classroom. The therapist can then monitor the child's progress through our application and use this information to identify a child's problems and tailor the therapy to them. This will save both time and money for school districts and parents who are paying for their child's therapy.

@@

The purpose of this paper and project is to make speech therapy more effective in English speaking children from age 5 to age 12. Common speech impediments in children are often caused by functional speech disorders, or trouble learning to make specific speech sounds \cite{Brown:Children}. Children in this age group tend to average over a year involved in weekly speech therapy meetings to overcome a speech disorder \cite{Kreider:Intro}. Speech therapists only get to work with a child for as little as half an hour a week where the child repeat words back to the therapist in order to target a specific sound or phoneme. With only short sessions like these, remote practice would be very beneficial to a child if they had a way to receive feedback and if a therapist could track a child's progress.

We chose to focus on `R' sounds as they are one of the more common mispronunciations found in our target age group \cite{Dodd:Children}. Most `R' disorders will commonly pronounce words as if the `R' is a `W'. An example would be pronouncing the word {\em ``rabbit''} as {\em ``wabbit''}. We use similar techniques as therapists use in their sessions in our online application. By having the child or user repeat a target several times until he or she is able to pronounce it correctly, we are emulating the in person setting that they are used to. Each time a word is spoken an audio recording of the speech is documented and saved for the therapist to analyze at a later time. This process is then wrapped in game setting to make the process of saying and repeating words more enjoyable for children. This helps supplement the therapy rather than aiming to replace it. We hope that this will cause a decrease in the amount of time that children will need to spend in therapy, which will help save the school district or parents more money.

@@

With the widespread use of the tablet and increasing availability of the Internet, several applications have been developed that are similar to {\em Kimbee}. Researchers at the University of Zaragoza have created a standalone tablet application that aims to remove the therapist from the treatment \cite{Carlos:Vocaliza}. The researchers created an application for children to speak words and receive feedback on whether the word they said matches what was on the screen. The model they used also requires the student to train his or her voice in order for it to be recognized and processed correctly. Because of this, the amount of time it would take a new student to get started is significant. Their application currently only supports the Spanish language, which would not be of much help to English speaking students. Our project's scope is much narrower. Our focus is to help the therapist spend higher quality time with his or her students by giving them additional information from the student's work outside the sessions.

@@

\section{Implementation}
